Growth Curves Paper

### 2020-03-13 R Analysis Scripts/CFU Data.Rmd
fixed some titles

```{r Confocal vs CFUs data wrangling}
#first pull confocal data:
##functions to read data
MapResults<- function(listSamples, reps){
  blah <-deparse(substitute(listSamples))
  mappedData<-map2(listSamples, reps, GetResults)
  boundData<-bind_rows(mappedData)
  boundData<-boundData %>% mutate(Strain = blah)
  boundData<-gather(boundData,"Color","Value",-Slice,-Position,-Sample,-TimePoint,-Strain) %>% mutate(LogValue=ifelse(Value>0,log10(Value),0))
  boundData<-boundData %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" )) %>% mutate(Species = recode(Color, "Red" = "Sa", "Green" = "Pa")) %>% mutate(ZDistance = Slice *0.44)
  boundData$Condition<-as.factor(boundData$Condition)
  boundData$Condition<-factor(boundData$Condition, levels = c("Sa Mono", "Pa Mono", "Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
  boundData$Species<-as.factor(boundData$Species)
  boundData$Strain<-as.factor(boundData$Strain)
  return(boundData)
  }
ReadResultsFile<-function(file, position, timepoint){
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Red', 'Green', 'Slice')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}
GetResults<-function(sample, samplename){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
  growthDf<-growthDf %>% mutate(Sample = samplename)
return(growthDf)
}

@@

##remove all the conditions I didn't do in the plate counts and fix time points:
DataComparisonScope<-allConfocalResultsStats %>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,3,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope

##remove stirred condition I didn't do in the scope and fix strain names:
DataComparisonCFU<-PA14DataStats %>% filter (condition == "Static") %>% select(bug, strain, CFUmean, logCFUmean, condition, time)%>% as.data.frame() 
DataComparisonCFU<-DataComparisonCFU%>% mutate(Strain = recode(DataComparisonCFU$strain, wt = "PA14wt", mut = "PA14mut"))

@@

##Adding more data from the TOB experiments!
#first select relevant conditions and fix column names
DataComparisonCFUSa<-newSCFMDataSa%>%  filter(!culture == "mono") %>% filter(antibiotic == "Control") %>% select(CFU, culture, bug, timePoint, antibiotic, logTranformed,sample, condition) %>% group_by(culture, timePoint) %>% summarise(meanCFU = mean(CFU), meanLogCFU = mean(logTranformed))

@@

colnames(DataComparisonCFUSa)<-c("strain", "time", "CFUs", "logCFUs", "Strain")
#then do the same for the scope data
DataComparisonScopeSa<-allConfocalResultsStats %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
#merge them!
comparisonSaDf <- merge(DataComparisonCFUSa,DataComparisonScopeSa,by=c("time","Strain"))

>>>>

```{r Confocal data wrangling}
#first pull confocal data:
##functions to read data
MapResults<- function(listSamples, reps){
  blah <-deparse(substitute(listSamples))
  mappedData<-map2(listSamples, reps, GetResults)
  boundData<-bind_rows(mappedData)
  boundData<-boundData %>% mutate(Strain = blah)
  boundData<-gather(boundData,"Color","Value",-Slice,-Position,-Sample,-TimePoint,-Strain) %>% mutate(LogValue=ifelse(Value>0,log10(Value),0))
  boundData<-boundData %>% mutate(Condition = recode(Position, "0" = "Sa Mono", "1" = "Pa Mono", "2" = "Pa:Sa 1:1", "3" = "Pa:Sa 10:1", "4" = "Pa:Sa 1:100", "5" = "Pa:Sa 1:10" )) %>% mutate(Species = recode(Color, "Red" = "Sa", "Green" = "Pa")) %>% mutate(ZDistance = Slice *0.44)
  boundData$Condition<-as.factor(boundData$Condition)
  boundData$Condition<-factor(boundData$Condition, levels = c("Sa Mono", "Pa Mono", "Pa:Sa 1:1", "Pa:Sa 1:10", "Pa:Sa 1:100","Pa:Sa 10:1"))
  boundData$Species<-as.factor(boundData$Species)
  boundData$Strain<-as.factor(boundData$Strain)
  return(boundData)
  }
ReadResultsFile<-function(file, position, timepoint){
  datos <-read.csv(file, header = FALSE)
  colnames(datos)<-c('Red', 'Green', 'Slice')
  datos<-datos %>% mutate(Position = position)
  datos<-datos %>% mutate(TimePoint = timepoint)
  return(datos)
}
GetResults<-function(sample, samplename){
  folder<- paste0('/Users/jupabago/Documents/Whiteley/PROJECTS/PaSaProject/Spatial paper Data/Microscopy Data/Other Data1/',sample,'/results')#the path needs to be "Other Data1"
  fileList<-list.files(path = folder, full.names = TRUE)
  growthDf<-data.frame()
  for (position in 0:5){
    currentPosition<-fileList[grep(paste0("p",position,"."),fileList)]
    for (timepoint in 0:17){
      currentTimePoint<-currentPosition[grep(paste0("t",GetNumber(timepoint),"_"),currentPosition)]
      growthDf<-rbind(growthDf,ReadResultsFile(currentTimePoint, position, timepoint))}}
  growthDf<-growthDf %>% mutate(Sample = samplename)
return(growthDf)
}

@@

##remove all the conditions I didn't do in the plate counts and fix time points:
DataComparisonScope<-allConfocalResultsStats %>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,3,7,11,15)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
```

```{r CFU data wrangling}
##remove stirred condition I didn't do in the scope and fix strain names:
DataComparisonCFU<-PA14DataStats %>% filter (condition == "Static") %>% select(bug, strain, CFUmean, logCFUmean, condition, time)%>% as.data.frame() 
DataComparisonCFU<-DataComparisonCFU%>% mutate(Strain = recode(DataComparisonCFU$strain, wt = "PA14wt", mut = "PA14mut"))

@@

##Adding more data from the TOB experiments!

#first select relevant conditions and fix column names
DataComparisonCFUSa<-newSCFMDataSa%>%  filter(!culture == "mono") %>% filter(antibiotic == "Control") %>% select(CFU, culture, bug, timePoint, antibiotic, logTranformed,sample, condition) %>% group_by(culture, timePoint) %>% summarise(meanCFU = mean(CFU), meanLogCFU = mean(logTranformed))

@@

colnames(DataComparisonCFUSa)<-c("strain", "time", "CFUs", "logCFUs", "Strain")

#then do the same for the scope data
DataComparisonScopeSa<-allConfocalResultsStats %>% filter(Species == "Sa")%>% filter (Strain %in% c("PA14wt","PA14mut")) %>% filter(Condition == "Pa:Sa 1:1") %>%  filter(TimePoint %in% c(0,2,3,4)) %>% select(Condition,TimePoint, Strain, Species, MeanTotals, MeanLogTotals) %>% mutate(time = ifelse(TimePoint>0, TimePoint+1, 0)) #The timePoint thing is because I start imaging after one hour and I don't have a time zero on scope
#merge them!
comparisonSaDf <- merge(DataComparisonCFUSa,DataComparisonScopeSa,by=c("time","Strain"))
